Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/Motiv.tex
centering figure 1

% !TEX root = main.tex
\section{Overview}
\label{sec:example}
\begin{figure}
	\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
	\tikzstyle{block1} = [draw, rectangle, minimum height=2em, minimum width=6em]
	\tikzstyle{block2} = [draw, rectangle, minimum height=1em, minimum width=4em]
	\tikzstyle{block3} = [draw, rectangle, minimum height=3.2em, minimum width=4em]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	{\centering

@@

		\draw [draw,->, align=center] (RMPC) -- node [left] {high-precision\\ controller}(Uij);
		\draw [->] (Uij) -- node [left] {$e$}(decide);
		\draw [->] (decide) -- node [left,pos=.3] {Yes} (done);
		\draw [->] (decide) -- node[pos=0.99] {} 
		node [] {No} (delta);
		\draw [->] (delta) |- node [above] {} (RMPC);
		\draw [->] (done) -- node [above] {} (output);
		%\node [block2, scale=0.7] at (1.3,-.42) {MATLAB} ;
		%\node [block2, scale=0.7] at (1.65,-2.95) {Daisy} ;
		%\node [block2, scale=0.7] at (1.58,-7) {Daisy} ;
		\end{tikzpicture}\par}
	%	\hspace{\fill} 
	%\end{center}
	%\end{adjustbox}
	\caption{High-level description of the proposed memory-efficient robust MPC design.}
	\label{fig:overview}
\end{figure}

>>>>

% !TEX root = main.tex
\section{Overview}
\label{sec:example}
\begin{figure}
\centering
	\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
	\tikzstyle{block1} = [draw, rectangle, minimum height=2em, minimum width=6em]
	\tikzstyle{block2} = [draw, rectangle, minimum height=1em, minimum width=4em]
	\tikzstyle{block3} = [draw, rectangle, minimum height=3.2em, minimum width=4em]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	{

@@

		\draw [draw,->, align=center] (RMPC) -- node [left] {High-precision controller}(Uij);
		\draw [->] (Uij) -- node [left] {$e$}(decide);
		\draw [->] (decide) -- node [left,pos=.3] {Yes} (done);
		\draw [->] (decide) -- node[pos=0.99] {} 
		node [] {No} (delta);
		\draw [->] (delta) |- node [above] {} (RMPC);
		\draw [->] (done) -- node [above] {} (output);
		%\node [block2, scale=0.7] at (1.3,-.42) {MATLAB} ;
		%\node [block2, scale=0.7] at (1.65,-2.95) {Daisy} ;
		%\node [block2, scale=0.7] at (1.58,-7) {Daisy} ;
		\end{tikzpicture}\par}
	%	\hspace{\fill} 
	%\end{center}
	%\end{adjustbox}
	\caption{Overview of the proposed memory-efficient robust MPC control design.}
	\label{fig:overview}
\end{figure}
